Phylogenetics and the human microbiome.

### 2013-09-26 sbreview.tex
blaser material

Preservation of diversity.
"Overall these studies reveal that human microbiome data has been preserved in some coprolites, and these preserved human microbiomes match more closely to those from the rural communities than to those from cosmopolitan communities. These results suggest that the modern cosmopolitan lifestyle resulted in a dramatic change to the human gut microbiome."

>>>>

Preservation of diversity.
\cite{blaser2011antibiotic,cho2012human}
"Overall these studies reveal that human microbiome data has been preserved in some coprolites, and these preserved human microbiomes match more closely to those from the rural communities than to those from cosmopolitan communities. These results suggest that the modern cosmopolitan lifestyle resulted in a dramatic change to the human gut microbiome."
